Comparative Evaluation of Spark and Flink Stream Processing

### 2017-02-19 paper/paper.tex
first version of introduction section

\par Big Data is now one of the hot topics in Information Technology, it has gained increasing attention of professionals in industry and academics, since the amount of data we generate is increasing exponentially. Moreover, recent years showed a rapid development of Big Data frameworks such as Spark and Flink that provide more and efficient data processing capabilities.
 \par The Big Data is a method to process not just only just large datasets (volume), but also that arrives in high rate (velocity), and it comes in all kinds of data format (variety) (i.e., 3Vs of Big Data (Volume, Velocity, Variety))\cite{svs}.

\par The processing models of Big Data are Batch and Stream processing, Batch processing is a way to handle large volumes of data (e.g., processing of historical transactions), is more concerned with throughput. While the Stream processing  is to manages fast and continues data (real-time) and processes it as it arrives (e.g., fraud detection and network monitoring applications), where the low latency is required.

>>>>

\par Big Data is now one of the hot topics in Information Technology, it has gained increasing attention of professionals in industry and academics, since the amount of data we generate is increasing exponentially; generated from social media platforms, mobile phones, IoT and finical transactions. Moreover, recent years showed a rapid development of Big Data frameworks such as Spark and Flink that provide more and efficient data processing capabilities.
 \par The Big Data is a method to process not just only just large datasets (volume), but also that arrives in high rate (velocity), and it comes in all kinds of data format (variety) (i.e., 3Vs of Big Data (Volume, Velocity, Variety))\cite{svs}.

\par The processing models of Big Data are Batch and Stream processing, Batch processing is a way to handle large volumes of data (e.g., processing of historical transactions), is more concerned with throughput. While the Stream processing  is to manages fast and continuously incoming data (real-time), processes it as it arrives (e.g., credit card fraud detection and network monitoring applications), where the low latency is required.
